Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-11 paper/paper.tex
pass on step2

For step 2, we considered using the open-source tool
eshost-cli~\cite{eshost-cli}, also used at Microsoft, for checking
output discrepancy. However, we noticed that eshost-cli does not
handle discrepancies involving crashes. As such, we forked the
eshost-cli GitHub project and implemented that functionality on it. It
is also important to note that our checker does not support the case
where the test fails in all engines but the kind of failure (\eg{},
exception thrown) is different. Currently, our infrastructure does not
report discrepancy for that case. For that, it would be necessary to
properly parse the error message to retrieve the error types. We left
that as future work as we already found several discrepancies even
without that.

>>>>

For step 2, we considered using the open-source tool
eshost-cli~\cite{eshost-cli}, also used at Microsoft, for checking
output discrepancy. However, we noticed that eshost-cli does not
handle discrepancies involving crashes, \Igor{If the criteria is to
find crashes or fatal errors, it is possible to run the
infrastructure with any runner(?) tool, including the
javascript binaries itself.}. As such, we forked the
eshost-cli GitHub project and implemented that functionality on it. It
is also important to note that our checker does not support the case
where the test fails in all engines but the kind of failure (\eg{},
exception thrown) is different. Currently, our infrastructure does not
report discrepancy for that case. For that, it would be necessary to
properly parse the error message to retrieve the error types. We left
that as future work as we already found several discrepancies even
without that.
